First Class Pattern Matching in a Deeply Embedded Domain Specific Language\\ \large{Not For Distribution}

### 2020-05-13 paper/paper.tex
Updated paper todos

Additionally, lambdas can also be difficult to implement in EDSLs. A major reason
for this is that control flow constructs which are typically \textit{outside} the EDSL,
such as pattern matching and tail recursion, can make it challenging to "look inside"
the lambda.
\begin{todo}
  Add brief summary of relationship to lambdas
\end{todo}

@@

@@

\section{Representing tail recursion}
\begin{todo}
  Expand the explanation in this section
\end{todo}

@@

\section{C Backend}
\begin{todo}
  Expand this section
\end{todo}

>>>>

Additionally, lambdas can also be difficult to implement in EDSLs. A major reason
for this is that control flow constructs which are typically \textit{outside} the EDSL,
such as pattern matching and tail recursion, can make it challenging to "look inside"
the lambda.
\begin{todo}
  Maybe add brief summary of relationship to lambdas?
\end{todo}

@@

\begin{todo}
  Write
\end{todo}

@@

\section{Representing tail recursion}
\begin{todo}
  Is the explanation in this section sufficient since we cite the Haskino paper,
  which describes how the tail recursion transformation was used in that project?
\end{todo}

@@

\section{C Backend}
\begin{todo}
  Should this section be expanded?
\end{todo}
